Personalization and probabilities: impersonal propensities in online grocery shopping

### 2018-05-16 reconstruction.rmd
starting proofs

One way in which recommender systems might attempt to address the problem of the relational dynamics of propensities is by assuming that purchases will be repeated.   Patel mentioned that the new model uses '52 weeks of data' for each customer. In including this data in the model, the assumption is that the probability that a specific customer will buy a specific product will be increased by previous purchases of that product. The history of previous purchases constitutes forms of repetition that imply a stabilisation of propensities (e.g. a vegan customer will never have purchased chicken products, so the measured propensities for any of the 1000 or so chicken products sold be Tesco will remain close to `0`). But the changing situation of the customer only figures here in the accumulated year of purchase data, and that past purchases might precisely what does not need to recommended.

>>>>

One way in which recommender systems might attempt to address the problem of the relational dynamics of propensities is by assuming that purchases will be repeated.   Patel mentioned that the new model uses '52 weeks of data' for each customer. In including this data in the model, the assumption is that the probability that a specific customer will buy a specific product will be increased by previous purchases of that product. The history of previous purchases constitutes forms of repetition that imply a stabilisation of propensities (e.g. a vegan customer will never have purchased chicken products, so the measured propensities for any of the 1000 or so chicken products sold be Tesco will remain close to `0`). But the changing situation of the customer only figures here in the accumulated year of purchase data.  Past purchases might precisely be  what does not need to be recommended.
